---
title: "e-Rum2020 CovidR Contest"
site: rmdgallery::gallery_site
---

<h1>Welcome to the CovidR Contest!</h1>


[**eRum2020::CovidR**](about.html) is an open-source contest and pre-conference event launched by the 2020 European R Users Meeting ([**e-Rum2020**](https://2020.erum.io/)), featuring any work done with R around the topic of the [**COVID-19 pandemic**](https://www.who.int/emergencies/diseases/novel-coronavirus-2019).

The pre-conference virtual event will take place on **May 29th**, when selected participants will be invited to present their work and the contest winners will be announced and awarded with e-prizes. Accepted contributions ([submitted](submit.html) before May 22nd) are made available in this website, where the wider community is invited to provide feedback. The winner(s) will be announced during the conference pre-event on **May 29th**. Attendance to the event is subject to a [**free registration**](https://www.eventbrite.it/e/covidr-erum-2020-pre-conference-event-tickets-104133026686), closing on **May 22nd**.

The set of **accepted submissions** feature the contributions below. The corresponding gallery pages allow the wider community to browse through and **like contributions**.

```{r, echo=FALSE}
meta <- rmdgallery::gallery_site_config()$gallery$meta

# Create YAML file with the dynamic label for the eRum2020::CovidR badges
short_list_status <- yaml::read_yaml("contributions/.short-list.yml")
shields_text <- lapply(meta, function(page_meta) {
  short_list_status[[page_meta$page_name]] %||% "Accepted"
})
yaml::write_yaml(shields_text, "badge-endpoint.yml")


# Create the list of contributions
# NOTE: We want to allow voting contributions directly from the list, however we
# cannot have one modal per contribution since utteranc.es seems to struggle
# when retrieving multiple issues simultaneously. As a workaround, we have only
# one modal that we update with page-specific utterances and content on click.

source(site_path("_tools", "vote-modal.R"))
vote_id <- "vote-modal"
utterances_repo <- "Milano-R/erum2020-covidr-contest"
site <- "erum2020-covidr-contest"
`%>%` <- bsplus::`%>%`
tags <- htmltools::tags

contributions_list <- function(meta) {
  tags$div(
    id = "contributions",
    # empty modal placeholder
    vote_modal(vote_id, title = "", repo = NULL),
    # loop over contributions
    lapply(names(meta), function(name) {
      details_id <- sprintf("details-%s", name)
      href <- sprintf("%s.html", name)
      one_meta <- meta[[name]]
      tags$div(
        class = "panel",
        htmltools::div(
          class = "btns",
          # details accordion button
          htmltools::tag(
            "button", list(
              class = "btn btn-badge collapsed",
              tags$span(class = "fa fa-minus"),
              `data-parent` = "#contributions"
            )
          ) %>% bsplus::bs_attach_collapse(., details_id),
          # voting modal button
          htmltools::tag(
            "button", list(
              title = "Vote for this contribution",
              class = "btn btn-badge",
              tags$span(class = "fa fa-thumbs-up"),
              # set page-specific voting modal content
              onclick = sprintf(
                "set_vote_modal(%s, %s, %s, %s)",
                deparse(vote_title(one_meta$title)),
                deparse(utterances_repo), deparse(site), deparse(one_meta$page_name)
              )
            )
          ) %>% bsplus::bs_attach_modal(., vote_id)
        ),
        # headline
        tags$a(
          href = href, one_meta$title
        ),
        "by", tags$em(one_meta$author),
        # details
        tags$div(
          class = "details collapse", id = details_id,
          tags$div(
            class = "abstract",
            tags$em("Abstract"), htmltools::HTML("&mdash;"),
            htmltools::HTML(gsub(
              "</?p>", "", # the code is wrapped inside <p></p> by markdownToHTML
              markdown::markdownToHTML(
                text = one_meta$abstract, fragment.only = TRUE
              )
            ))
          ),
          tags$div(
            class = "repo",
            tags$em("Repository"), htmltools::HTML("&mdash;"),
            tags$a(
              one_meta$repository, href = one_meta$repository, target = "_blank"
            )
          ),
        )
      )
    })
  )
}

```

<hr>

The following contributions have been selected as **CovidR contest finalists**, and will be **presented at the e-Rum2020 pre-conference event** on May 29th.

```{r, echo=FALSE}
# sorted as in short_list
contributions_list(meta[intersect(names(short_list_status), names(meta))])
```

The other **accepted contributions** are listed below.

```{r, echo=FALSE}
contributions_list(meta[!names(meta) %in% names(short_list_status)])
```
